Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations

### 2018-01-15 Thesis/Thesis.rnw
Added calendrical rounding analysis and rewrote conclusions

% Agenda
%  * Round time periods pre-coverage analysis in order to make conclusion make sense
% 
% Todo
%  * Change how mod 52-1/7 is done
%  * "Coverage" -> preventable fraction
%  * "Statewide"

<<options, echo=FALSE>>=
    opts_chunk$set(echo=FALSE, message=FALSE, root.dir=".texpadtmp")
@

<<load>>=
library(reshape)
library(dplyr)
library(mgcv)
library(outbreakpredict)
library(zipcode)
library(ggplot2)
library(easyGgplot2)
library(data.table)
library(splitstackshape)

read_chunk("../Analysis/RSV.R")
read_chunk("../Thesis/Thesis.R")
@

@@

\input{structure.tex}

@@

@@

\abstractsection{Results} At 95\% confidence level, we found alternate regimens that account for spatial variability of RSV incidence at the county level to have superior coverage (to that of the AAP-recommended regimen) in some regions of Connecticut, and non-inferior coverage in other regions. We also found alternate regimens that account for temporal RSV variability at the annual level to have non-superior coverage to our spatially-adjusted regimens. Overall, we found our best-performing spatially-adjusted alternate to AAP guidelines to provide a XX\% state-wide increase in RSV prophylaxis coverage over the AAP regimen.

@@

\listoftables
\clearpage

@@

TODO

@@

\begin{itemize}
	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
	\item Can we use spatial analysis of RSV to propose alternate regimens, either state-wide or regional, that would improve effectiveness over AAP-recommended prophylaxis, without increasing treatment cost?
	\item Is there year-to-year variation in timing of RSV season in Connecticut?
	\item Can we take advantage of any year-to-year variation to improve upon AAP-recommended prophylaxis, without increasing treatment cost?
\end{itemize}

@@

Due to changes in diagnostic coding, we excluded data prior to July 1996; surveillance year 2014 had incomplete data and was also excluded.

@@

@@

For the three alternate regimens based on state-wide data, we estimated preventable fraction statewide, as well as in each region.

For the three alternate regimens based on regional data, we estimated coverage in the corresponding region.

% TODO Consider also reporting net statewide coverage of regional regimens

@@

@@

Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)}) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)}), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)}) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)}). (Figure \ref{fig:seasonByRegion}.)

@@

\begin{figure}
<<seasonByRegion, results='hide'>>=
    data = thresholdsByCounty %>% 
        filter(county %in% countiesForPlots) %>%
        melt(id=c("county")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=c("onset", "offset"))) %>%
        cast(county + variable ~ pctile)

    tikz("figure/seasonByRegion.tex", width=plotWidth, height=plotHeight, pointsize=10)
    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
        geom_point(aes(y=median, x=county)) + 
        labs(aes(x=variable)) +
        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
        labs(y="Surveillance week") + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
        )
    dev.off()
@
\begin{center}
\input{figure/seasonByRegion.tex}
\caption{Onset and offset of RSV season in Connecticut by region}
\label{fig:seasonByRegion}
\end{center}
\end{figure}

@@

Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)}); season offset shows no change from the statewide median. (Figure \ref{fig:seasonByRegion}.)

@@

Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap")} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}) occur while palivizumab, administered according to AAP guidelines, offers protection. The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap")} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap")} cases ((\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", level)})) occur during this time. (Table \ref{table:coverageByRegionAAP}.)

\begin{figure}
<<coverageByRegionAAP, results='hide'>>=
    tikz("figure/coverageByRegionAAP.tex", width=plotWidth, height=plotHeight, pointsize=10)
    ggplot(unprotectedByCounty %>% filter(strat=="aap") %>% filter(county %in% countiesForPlots)) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
        geom_point(aes(y=frac.median, x=county)) + 
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        labs(y="Preventable fraction") +
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank()
        )
    dev.off()
@
\input{figure/coverageByRegionAAP.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region.}
\label{fig:coverageByRegionAAP}
\end{figure}

The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}; temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of AAP prophylaxis regimen. Fairfield county, owing to its early season onset, has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset, have their RSV seasons almost entirely contained within the prophylaxis window.

\begin{figure}
<<coverageByRegionAAPInsight, results='hide'>>=
    tikz("figure/coverageByRegionAAPInsight.tex", width=plotWidth, height=plotHeight*3/2, pointsize=10)
    ggplot2.multiplot(plotlist=lapply(countiesForPlots, function(c) {
        strat = ppxFixedStrategies("all")[["aap"]]

        countyPred = predByCounty %>% filter(county==c) %>% mutate(ppx=strat(time))
        countyThresholds = thresholdsByCounty %>% filter(county==c)
        ppxStart = min((countyPred %>% filter(ppx > 0))$time)
        ppxEnd = max((countyPred %>% filter(ppx > 0))$time)

        unprotectedAtStart = (countyPred %>% filter(time==ppxStart))$rsv.cum.fit
        unprotectedAtEnd = (countyPred %>% filter(time==ppxEnd))$rsv.cum.fit

        annotation_timespan = function(plot, xmin, xmax, y, color, label) {
            ymin = y - .01
            ymax = y + .01
            yminlabel = y + .01
            ymaxlabel = y + .11
            plot + annotation_custom(linesGrob(gp=gpar(col=color)), xmin=xmin, ymin=y, xmax=xmax, ymax=y) + 
            annotation_custom(linesGrob(gp=gpar(col=color)), xmin=xmin, ymin=ymin, xmax=xmin, ymax=ymax) + 
            annotation_custom(linesGrob(gp=gpar(col=color, lty="dotted")), xmin=xmin, ymin=0, xmax=xmin, ymax=1) + 
            annotation_custom(linesGrob(gp=gpar(col=color)), xmin=xmax, ymin=ymin, xmax=xmax, ymax=ymax) + 
            annotation_custom(linesGrob(gp=gpar(col=color, lty="dotted")), xmin=xmax, ymin=0, xmax=xmax, ymax=1) + 
#            annotation_custom(linesGrob(gp=gpar(col=color)), xmin=(xmin + xmax) / 2, ymin=y-0.02, xmax=(xmin + xmax) / 2, ymax=y+0.02) + 
            annotation_custom(textGrob(label, gp=gpar(col=color)), xmin=xmin, xmax=xmax, ymin=yminlabel, ymax=ymaxlabel)
        }

        plot = ggplot(countyPred) +
            geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25))
        plot = plot %>%
            annotation_timespan(ppxStart, ppxEnd, 1.05, hsv(1/3, 1, .5), "Prophylaxis") %>%
            annotation_timespan(countyThresholds$onset.median, countyThresholds$offset.median, -0.05, hsv(0, 1, .5), "RSV Season")
        plot = plot + 
            annotate("segment", x=-Inf, y=unprotectedAtStart, xend=ppxStart, yend=unprotectedAtStart, linetype=3) + 
            annotate("segment", x=-Inf, y=unprotectedAtEnd, xend=ppxEnd, yend=unprotectedAtEnd, linetype=3) + 
            scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(0, 1), expand=c(0.2, 0)) +
            labs(x=c) +
            theme(
                axis.title.y=element_blank(),
                axis.ticks.x=element_blank()
            )
        table = ggplot_gtable(ggplot_build(plot))
        table$layout$clip[table$layout$name == "panel"] <- "off"

        plot
    }), cols=2)
    dev.off()
@
\input{figure/coverageByRegionAAPInsight.tex}
\caption{RSV relative cumulative incidence by region}
\label{fig:coverageByRegionAAPInsight}
\end{figure}

@@

Based on all-years data, the six spatially adjusted prophylaxis regimens, when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county. (Figure \ref{fig:coverageByRegion}.)

Statewide, the AAP guidelines generate protection for \Sexpr{regionStrategyCoverage("all", "aap")} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}); meanwhile, the regimens based on all-years statewide onset produce the weakest improvement at \Sexpr{regionStrategyCoverage("all", "stateOnset")} coverage (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", level)}), and other alternate regimens yield similar results.

In Hartford county, the improvement is more noteworthy. Here, the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap")} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", level)}); the regimens based on all-years regional offset generate the weakest improvement to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset")} protection (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", level)}), and other alternate regimens are comparable.

@@

\begin{figure}
<<coverageByRegion, results='hide', warning=FALSE>>=
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots)
    tikz("figure/coverageByRegionRegimen.tex", width=plotWidth, height=plotHeight, pointsize=10)
    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_linetype_manual(values=c(1, 3, 4, 2, 3, 4, 2)) + 
        scale_color_manual(values=c(grey(0), rep(hsv(0, 1, 1), 3), rep(hsv(4/6, 1, 1), 3))) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, linetype=strat, color=strat, group=strat), 
            width=0, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5)) +
        geom_point(aes(y=frac.lower, x=county, color=strat), position=position_dodge(.5), shape=18) +
        geom_point(aes(y=frac.upper, x=county, color=strat), position=position_dodge(.5), shape=18) +
        labs(y="Preventable fraction") +
        guides(color=guide_legend(keywidth=3, keyheight=1), linetype=guide_legend(keywidth=3, keyheight=1)) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@
\input{figure/coverageByRegionRegimen.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen.}
\label{fig:coverageByRegionRegimen}
\end{figure}

\paragraph{RSV season onset and offset are unchanged over time}

Our linear regression of median surseason onset and offset against surseason year (Figure \ref{fig:onsetOffsetByYear}) indicates (at 95\% confidence level) that season onset has not been drifting earlier (\Sexpr{formatDriftCI(onsetByYear, level)}), and neither has season offset (\Sexpr{formatDriftCI(offsetByYear, level)}).

\begin{figure}
<<onsetOffsetByYear, results='hide', warning=FALSE>>=
    data = stateThresholdsByWindow %>% 
        melt(id=c("year")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=c("onset", "offset"))) %>%
        cast(year + variable ~ pctile)

    tikz("figure/onsetOffsetByYear.tex", width=plotWidth, height=plotHeight, pointsize=10)
    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymin=lower, ymax=upper, x=year), width=.1) + 
        geom_point(aes(y=median, x=year)) +
        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
        scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
        labs(y="Surveillance week") + 
        theme(
            axis.title.x=element_blank()
        )

    dev.off()
@
\input{figure/onsetOffsetByYear.tex}
\caption{RSV season onset and offset by three-year surseason.}
\label{fig:onsetOffsetByYear}
\end{figure}

@@

Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-incidence counties, where they produced inferior results. (TODO: Figure.) TODO: specifics

>>>>

% TODO: DOI in bib?
% TODO: Prettier abstract sectioning
% TODO: Better calendrical cues in plots

<<options, echo=FALSE>>=
    opts_chunk$set(echo=FALSE, message=FALSE)
@

<<load>>=
read_chunk("../Analysis/RSV.R")
read_chunk("../Thesis/Thesis.R")
@

<<libraries, cache=FALSE>>=
@

@@

\input{structure.tex}
\edef\figuresDir{\Sexpr{figuresDir}}

@@

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

@@

\abstractsection{Results} At 95\% confidence level, we found alternate regimens that account for spatial variability of RSV incidence at the county level to have superior coverage (to that of the AAP-recommended regimen) in some regions of Connecticut, and non-inferior coverage in other regions. We also found alternate regimens that account for temporal RSV variability at the annual level to have non-superior coverage to our spatially-adjusted regimens. Overall, we found our best-performing spatially-adjusted alternate to AAP guidelines to provide a XX\% statewide increase in RSV prophylaxis coverage over the AAP regimen.

@@

%\listoftables
%\clearpage

@@

RSV seasonality has been established throughout the United States, with a stable onset between mid-November and early January and a stable offset between mid-March and late April in all states except for Florida, based on National Respiratory and Enteric Virus Surveillance System data.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}

@@

\begin{itemize}
	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
	\item Can we use spatial analysis of RSV to propose alternate regimens, either statewide or regional, that would improve effectiveness over AAP-recommended prophylaxis, without increasing treatment cost?
	\item Is there year-to-year variation in timing of RSV season in Connecticut?
	\item Can we take advantage of any year-to-year variation to improve upon AAP-recommended prophylaxis, without increasing treatment cost?
\end{itemize}

@@

Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data starting after June 2013, due to incompleteness.

@@

% TODO: map

@@

For the three alternate regimens based on statewide data, we estimated preventable fraction statewide, as well as in each region.

For the three alternate regimens based on regional data, we estimated preventable fraction in the corresponding region.

\subsection{Accommodating implementation complexity}

Keeping in mind implementation constraints of clinical practice guidelines, we performed three additional variants of our spatial analysis:

\begin{itemize}
    \item \textbf{Weekly rounding}: prophylaxis start and end date rounded to the nearest calendar week,
    \item \textbf{Biweekly rounding}: prophylaxis start and end date rounded to the nearest two-week calendar period, with two-week period boundary chosen , and % TODO: specifics
    \item \textbf{Monthly rounding}: prophylaxis start and end date rounded to the nearest four-week calendar period.  % TODO: specifics and also not actually in code now
\end{itemize}

In each variant, we again estimated the preventable fraction of all six spatially-adjusted regimens.

@@

\setcounter{figure}{1}
\begin{figure*}
<<coverageByRegionAAPInsight, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAPInsight.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight, pointsize=10)

    strat = ppxFixedStrategies("all")[["aap"]]

    data = predByCounty %>%
	    filter(county %in% countiesForPlots)

    thresholds = data %>%
    	mutate(ppx=strat(time)) %>%
    	filter(ppx > 0) %>%
    	group_by(county) %>%
    	do(
    		data.frame(
    			ppx.start=min(.$time),
    			ppx.end=max(.$time),
    			unprotected.start=min(.$rsv.cum.fit),
    			unprotected.end=max(.$rsv.cum.fit)
    		)
    	) %>%
    	ungroup() %>%
    	as.data.frame() %>%
    	inner_join(thresholdsByCounty, by="county")

    barYmin = 0.025
    barYmax = 0.075

    spanExtents = data.frame(
        variable=c("ppx", "season"), 
        barYmin=c(1 + barYmin, -barYmax), 
        barYmax=c(1 + barYmax, -barYmin), 
        lineYmin=c(0, -barYmin), 
        lineYmax=c(1 + barYmin, 1)
    )

    spans = thresholds %>%
        select(county, matches("ppx."), matches(".median")) %>%
        rename(season.start=onset.median, season.end=offset.median) %>%
        melt(id.vars="county") %>%
        cSplit("variable", ".") %>%
        rename(variable=variable_1, part=variable_2) %>%
        cast(county + variable ~ part) %>%
        right_join(spanExtents, by="variable")

    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"))

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), linetype="11", data=spans) + 
    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), linetype="11", data=spans) + 
    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans) + 
    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype=3, data=thresholds) + 
        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype=3, data=thresholds) + 
        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
        scale_color_manual(labels=spanLabels, values=twoTone) +
        scale_fill_manual(labels=spanLabels, values=twoTone) +
        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
        facet_wrap(~county, ncol=5) +
        labs(x="Surveillance week") + 
        theme(
            legend.title=element_blank(),
            axis.title.y=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )

    dev.off()
@
\input{\figuresDir/coverageByRegionAAPInsight.tex}
\caption{Weekly RSV relative cumulative incidence in Connecticut, by region}
\label{fig:coverageByRegionAAPInsight}
\end{figure*}
\setcounter{figure}{0}

@@

Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks). (Figure \ref{fig:seasonByRegion}.)

@@

@@

Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median. (Figure \ref{fig:seasonByRegion}.)

\begin{figure}
<<seasonByRegion, results='hide'>>=
    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    data = thresholdsByCounty %>% 
        filter(county %in% countiesForPlots) %>%
        melt(id=c("county")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
        cast(county + variable ~ pctile)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
        geom_point(aes(y=median, x=county)) + 
        labs(aes(x=variable)) +
        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
        labs(y="Surveillance week") + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
        )
    dev.off()
@
\begin{center}
\input{\figuresDir/seasonByRegion.tex}
\caption{RSV season onset and offset in Connecticut, by region}
\label{fig:seasonByRegion}
\end{center}
\end{figure}
\setcounter{figure}{2}

@@

Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered according to AAP guidelines, offers protection.

The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time. (Figure \ref{fig:coverageByRegionAAP}.)

\begin{figure}
<<coverageByRegionAAP, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)

    data = unprotectedByCounty %>% 
        filter(strat=="aap", rounding==0) %>% 
        filter(county %in% countiesForPlots)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
        geom_point(aes(y=frac.median, x=county)) + 
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        labs(y="Preventable fraction") +
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank()
        )
    dev.off()
@
\input{\figuresDir/coverageByRegionAAP.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region}
\label{fig:coverageByRegionAAP}
\end{figure}

The cause of this is evident in figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of the AAP-recommended prophylaxis regimen. Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.

@@

Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county. (Figure \ref{fig:coverageByRegionRegimen}.)

Statewide, the AAP guidelines offer protection for \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}); meanwhile, the regimens based on all-years statewide onset produce the weakest improvement at \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} coverage (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}), and other alternate regimens yield similar results.

In Hartford county, the improvement is similar. Here, the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}); the regimens based on all-years regional offset generate the weakest improvement to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} protection (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}), and other alternate regimens are comparable.

@@

\begin{figure*}
<<coverageByRegion, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE)

    stratLabels = legendLabels(c(
        "Statewide onset", "Statewide midseason", "Statewide offset", 
        "Regional onset", "Regional midseason", "Regional offset", 
        "Statewide recent-years onset", "Statewide recent-years midseason", "Statewide recent-years offset", 
        "AAP guidelines"
    ))

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@
\input{\figuresDir/coverageByRegionRegimen.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
\label{fig:coverageByRegionRegimen}
\end{figure*}

\paragraph{Calendrical rounding rapidly erases gains over the AAP-recommended regimen}

\begin{figure*}
<<coverageByRounding, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)

    data = unprotectedByCounty %>% 
        filter(county == "all", sliding==FALSE)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.935, 0.965), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
        scale_x_discrete(labels=roundingLabels) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=rounding, color=strat), position=position_dodge(.5), size=.75) +
        labs(x="Calendrical rounding", y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        theme(
            legend.position="bottom"
        )
    dev.off()
@
\input{\figuresDir/coverageByRoundingRegimen.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by calendrical rounding of prophylaxis regimen}
\label{fig:coverageByRoundingRegimen}
\end{figure*}

\begin{figure*}
<<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat))

    stratLabels = legendLabels(c(
        "Statewide all-years onset", "Statewide all-years midseason", "Statewide all-years offset", 
        "Regional onset", "Regional midseason", "Regional offset", 
        "Statewide recent-years onset", "Statewide recent-years midseason", "Statewide recent-years offset", 
        "AAP guidelines"
    ))

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(rep(twoTone, each=3), grey(0))) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@
\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
\label{fig:coverageByRegionRegimenWithSliding}
\end{figure*}

After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternate immunoprophylaxis regimens, overall we found that longer rounding intervals diminished the net benefit of spatial analysis.

With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide. The increase was most notable in Fairfield and Hartford counties. % TODO Details?

Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide. The increase was most notable in Fairfield and New Haven counties. % TODO Details?

However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}). With this rounding, all our regimens were non-superior to the AAP-recommended regimen in all regions.

\paragraph{RSV season onset is slowly moving earlier}

Our linear regression of median surseason onset and offset against surseason year (Figure \ref{fig:onsetOffsetByYear}) indicates that season onset has slowly been drifting earlier, at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}). It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.

Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).

\begin{figure}
<<onsetOffsetByYear, results='hide', warning=FALSE>>=
    data = stateThresholdsByWindow %>% 
        melt(id=c("epiyear")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
        cast(epiyear + variable ~ pctile)

    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymin=lower, ymax=upper, x=epiyear), width=.1) + 
        geom_point(aes(y=median, x=epiyear)) +
        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
        scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
        labs(y="Surveillance week") + 
        theme(
            axis.title.x=element_blank()
        )

    dev.off()
@
\input{\figuresDir/onsetOffsetByYear.tex}
\caption{RSV season onset and offset in Connecticut, by three-year surseason}
\label{fig:onsetOffsetByYear}
\end{figure}

@@

Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-incidence counties, where they produced inferior results. (Figure \ref{fig:coverageByRegionRegimenWithSliding}.)
